A systematic search for transiting planets in the \KT\ data

### 2015-03-17 ms.tex
fixing #27

\newcommand{\BIC}{{\ensuremath{\mathrm{BIC}}}}
\newcommand{\TIC}{{\ensuremath{\mathrm{TIC}}}}
\newcommand{\T}{\ensuremath{\mathrm{T}}}
\newcommand{\dd}{\ensuremath{\,\mathrm{d}}}
\newcommand{\bvec}[1]{{\ensuremath{\boldsymbol{#1}}}}
\newcommand{\appropto}{\mathrel{\vcenter{
  \offinterlineskip\halign{\hfil$##$\cr
    \propto\cr\noalign{\kern2pt}\sim\cr\noalign{\kern-2pt}}}}}
\newcommand{\densityunit}{{\ensuremath{\mathrm{nat}^{-2}}}}

@@

In general, the variable depth model will \emph{always} get a higher
likelihood because it is more flexible.
Therefore, a formal model comparison is required to compete these two models
against each other on equal footing.
For computational simplicity and speed, we use the Bayesian Information
Criterion (BIC).
The traditional definition of the BIC is
\begin{eqnarray}
-\frac{1}{2}\,\BIC &=&
    \ln p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration)
    - \frac{K}{2} \ln N
\end{eqnarray}
where the likelihood function is evaluated at the maximum, $K$ is an estimate
of the model complexity and $N$ is the effective sample size.
To emphasize that $K$ and $N$ are tuning parameters of the method, we
rewrite the BIC as something that we'll call the ``TIC''
\begin{eqnarray}
\TIC &=&
    \ln p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) -
        \frac{J\,\alpha}{2}
\end{eqnarray}
where $J$ is the number of allowed depths---one for the constant depth model
and the number of transits for the variable depth model---and $\alpha$ is
chosen heuristically.
For the K2 Campaign~1 dataset, we find that $\alpha \sim 1240$ leads to
reliable recovery of injected signals while still being fairly insensitive to
false signals.

To limit memory consumption, in the periodic search, we profile (or maximize)
over \phase\ and \duration\ subject to the constraint that
$\TIC_\mathrm{const} > \TIC_\mathrm{var}$ and requiring that the signal have
at least two observed transits.
This yields a one-dimensional spectrum of the signal-to-noise of the depth
measurement as a function of period using Equations~(\ref{eq:periodic-depth})
and (\ref{eq:periodic-depth-uncert}) to compute $\depth/\sigma_\depth$ at
each period.
The result is a generalization of the \project{BLS} frequency spectrum
\citep{Kovacs:2002} to a light curve model that includes both a transit and the
trends.
For example, \fig{periodic} shows the spectrum for a planet candidate
transiting EPIC 201613023.

@@

The periodic search procedure returned three signals per target so this gave
an initial list of 65,109 candidates.
The vast majority of these signals are not induced by a transiting planet:
there are many false positives.
Therefore to reduce the search space, we estimate the signal-to-noise of each
candidate by comparing the peak height to a robust estimate of variance in
\TIC\ values across period.
This is not the same criterion used to select the initial three peaks but we
find that it produces a more complete and pure sample.
A cut in this quantity can reject most variable stars and low signal-to-noise
candidates that can't be reliably recovered from the data.
To minimize contamination from false alarms but maximize our sensitivity, we
choose a threshold of 15.
We also find that the signals with periods $\lesssim 4$ days are strongly
contaminated by false alarms.
This might be because of the fact that our independence assumption
(\eqalt{indtran}) breaks down at these short periods.
Therefore, we discard all signals with periods shorter than 4 days,
acknowledging this will cause us to miss some planets
\citep{Sanchis-Ojeda:2014}.
After these cuts, 741 candidates remain; we examine these signals by hand.
The full list of peaks and their relevant meta data is available online
at\footnote{\datareleaseurl}.

@@

\acknowledgments
It is a pleasure to thank
Eric Agol (UW),
Ruth Angus (Oxford),
Tom Barclay (Ames),
Zach Berta-Thompson (MIT),
G\'eza Kov\'acs (Konkoly Observatory),
Laura Kreidberg (Chicago),
Erik Petigura (Berkeley),
Roberto Sanchis Ojeda (Berkeley),
and
Andrew Vanderburg (Harvard)
for helpful contributions to the ideas and code presented here.
DFM, DWH, and DW were partially supported by the National Science Foundation
(grant IIS-1124794),
the National Aeronautics and Space Administration
(grant NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
BTM was supported by a National Science Foundation Graduate Research
Fellowship (grant DGE‐1144469).

>>>>

\newcommand{\BIC}{{\ensuremath{\mathrm{BIC}}}}
\newcommand{\T}{\ensuremath{\mathrm{T}}}
\newcommand{\dd}{\ensuremath{\,\mathrm{d}}}
\newcommand{\bvec}[1]{{\ensuremath{\boldsymbol{#1}}}}
\newcommand{\appropto}{\mathrel{\vcenter{
  \offinterlineskip\halign{\hfil$##$\cr
    \propto\cr\noalign{\kern2pt}\sim\cr\noalign{\kern-2pt}}}}}
\newcommand{\densityunit}{{\ensuremath{\mathrm{nat}^{-2}}}}

@@

In general, the variable depth model will \emph{always} get a higher
likelihood because it is more flexible.
Therefore, a formal model comparison is required to compete these two models
against each other on equal footing.
For computational simplicity and speed, we use the Bayesian Information
Criterion (BIC).
The traditional definition of the BIC is
\begin{eqnarray}
-\frac{1}{2}\,\BIC &=&
    \ln p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration)
    - \frac{K}{2} \ln N
\end{eqnarray}
where the likelihood function is evaluated at the maximum, $K$ is an estimate
of the model complexity and $N$ is the effective sample size.
To emphasize that $K$ and $N$ are tuning parameters of the method, we
rewrite this equation as
\begin{eqnarray}
-\frac{1}{2}\,\BIC &=&
    \ln p(\{\flux\}_n\,|\,\period,\,\phase,\,\duration) -
        \frac{J\,\alpha}{2}
\end{eqnarray}
where $J$ is the number of allowed depths---one for the constant depth model
and the number of transits for the variable depth model---and $\alpha$ is
chosen heuristically.
For the K2 Campaign~1 dataset, we find that $\alpha \sim 1240$ leads to
reliable recovery of injected signals while still being fairly insensitive to
false signals.

To limit memory consumption, in the periodic search, we profile (or maximize)
over \phase\ and \duration\ subject to the constraint that
$\BIC_\mathrm{const} < \BIC_\mathrm{var}$ and requiring that the signal have
at least two observed transits.
This yields a one-dimensional spectrum of the signal-to-noise of the depth
measurement as a function of period using Equations~(\ref{eq:periodic-depth})
and (\ref{eq:periodic-depth-uncert}) to compute $\depth/\sigma_\depth$ at
each period.
The result is a generalization of the \project{BLS} frequency spectrum
\citep{Kovacs:2002} to a light curve model that includes both a transit and the
trends.
For example, \fig{periodic} shows the spectrum for a planet candidate
transiting EPIC 201613023.

@@

The periodic search procedure returned three signals per target so this gave
an initial list of 65,109 candidates.
The vast majority of these signals are not induced by a transiting planet:
there are many false positives.
Therefore to reduce the search space, we estimate the signal-to-noise of each
candidate by comparing the peak height to a robust estimate of variance in
\BIC\ values across period.
This is not the same criterion used to select the initial three peaks but we
find that it produces a more complete and pure sample.
A cut in this quantity can reject most variable stars and low signal-to-noise
candidates that can't be reliably recovered from the data.
To minimize contamination from false alarms but maximize our sensitivity, we
choose a threshold of 15.
We also find that the signals with periods $\lesssim 4$ days are strongly
contaminated by false alarms.
This might be because of the fact that our independence assumption
(\eqalt{indtran}) breaks down at these short periods.
Therefore, we discard all signals with periods shorter than 4 days,
acknowledging this will cause us to miss some planets
\citep{Sanchis-Ojeda:2014}.
After these cuts, 741 candidates remain; we examine these signals by hand.
The full list of peaks and their relevant meta data is available online
at\footnote{\datareleaseurl}.

@@

\acknowledgments
It is a pleasure to thank
Eric Agol (UW),
Ruth Angus (Oxford),
Tom Barclay (Ames),
Zach Berta-Thompson (MIT),
Daniel Bramich (QEERI, Qatar),
G\'eza Kov\'acs (Konkoly Observatory),
Laura Kreidberg (Chicago),
Erik Petigura (Berkeley),
Roberto Sanchis Ojeda (Berkeley),
and
Andrew Vanderburg (Harvard)
for helpful contributions to the ideas and code presented here.
DFM, DWH, and DW were partially supported by the National Science Foundation
(grant IIS-1124794),
the National Aeronautics and Space Administration
(grant NNX12AI50G), and the Moore--Sloan Data Science Environment at NYU.
BTM was supported by a National Science Foundation Graduate Research
Fellowship (grant DGE‐1144469).
